---
title: "About Section"

output: md_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

#### Overview 


This App can be used to predict a milestone event time (date of certain number of events occurs) for clinical trial monitoring.  Please see reference below for the methods used behind this App.  


#### Data  



* The Milestone App supports .csv, .tsv, .txt, .xlsx, .xls, .sas7bdat files. 
* Any uploaded data should contain 3 columns; 
    1. Column 1: Days of patient enrollment since first patient enrolled (i.e. date of patient enrolled minus the date of first patient enrolled).  Note, the first patient enrolled for the study would have 0 day. 
    2. Column 2: Days of patient last known event status time since first patient enrolled (i.e. date of patient last know event status minus the date of first patient enrolled).
    3. Column 3: Event indicator (1=event, 0=censored).
    
#### Disclaimer
Mayo Clinic does not save any of the data or output.
    

```{r, echo=FALSE, comment="", message=FALSE, results='markup'}
# readr::read_csv(here::here("sample.csv")) %>% 
#   mutate(sort = runif(nrow(.), 0, 1)) %>% 
#   arrange(sort) %>% 
#   select(-sort) %>% 
#   head(10)
```
