---
title: "About Section"
author: Brendan Thomas Broderick 
output: md_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

#### Overview 


This App is used to predict a milestone event date for Clinical Trial recruitment.  The methods used in this App can be found at [link](www.rstudio.com)   


#### References  


[1](www.rstudio.com)  Last, First M., and First M. Last. "Article Title." Journal Title Series Volume. Issue (Year Published): Page(s). Print.

[2](www.rstudio.com)  Last, First M., and First M. Last. "Article Title." Journal Title Series Volume. Issue (Year Published): Page(s). Print.  



#### Data  



* The Milestone App supports .csv, .tsv, .txt, .xlsx, .xls, .sas7bdat files. 
* Any uploaded data should contain 3 columns; 
    (1) Days from the opening of the Clinical Trial a patient was enrolled 
    (2) Days from opening of Clinical Trial patient had event (0 if no event)
    (3) An event indicator (0 or 1).

```{r, echo=FALSE, comment="", message=FALSE, results='markup'}
readr::read_csv(here::here("sample.csv")) %>% 
  mutate(sort = runif(nrow(.), 0, 1)) %>% 
  arrange(sort) %>% 
  select(-sort) %>% 
  head(10)
```
